---
title: "Standardized Effect Size"
author: "Joshua"
date: "2023-10-13"
output: html_document
---

# Packages
```{r echo = FALSE, print = FALSE, message = FALSE}
library("tidyverse")
library("ie2misc") # madstat mean absolute deviation
library("ggplot2")
library("gghalves")
library("cowplot")
library("ggpmisc") # adds stat_poly_eq to regression in ggplot
library("car") # for leveneTest (variance equality)
```

# Merging data and filtering species
```{r}
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)
chem_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_chemical_traits_2022.txt", guess_max = Inf)

chem_traits <- chem_traits %>% group_by(ID_merged, trait) %>% sample_n(1) 
chem_traits <- chem_traits %>% ungroup() %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("c_percent", "n_percent", "c_n", "d15n", "d13c")) # no sample removed, but trait phosphorus percentage removed because of missing data

traits <- raw_traits %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("ldmc", "leaf_area_cm2", "leaf_thickness_mm", "plant_height_cm", "sla_cm2_g")) # one sample removed: DLL3549
traits <- rbind(traits, chem_traits)

selected_sp <- traits %>% select(siteID, warming, species) %>% unique() %>% group_by(species) %>% mutate(Freq = n()) %>%
               filter(Freq >= 4 & species != "Achillea millefolium") # filtering species we have samples for in C and W for each site. n = 13. 2 sites n = 17. Not included is Achillea millefolium because it has warming samples only in Gud
selected_sp <- unique(selected_sp$species)
traits <- traits %>% filter(species %in% selected_sp) %>% mutate(species = ifelse(species == "Anthoxanthum odoratum", "Anthoxanthum alpinum", species))

rm(chem_traits, raw_traits, selected_sp)
```

# Cluster analysis
```{r}
# tutorial and blog post by David Zeleny: https://www.davidzeleny.net/anadat-r/doku.php/en:hier-agglom_examples
library("factoextra") # dist, fviz_dend
library("NbClust") # NbClust
library("psych") # pairs.panel
library("ggfortify") # autoplot

# tables of mean trait values per species, either all (all samples) or ctrl (only control samples) and either 5 traits or 4 traits
#sp_mean_all5 <- traits %>% filter(trait %in% c("plant_height_cm", "leaf_area_cm2", "leaf_thickness_mm", "ldmc", "sla_cm2_g")) %>%
                select(c(species, trait, value)) %>% group_by(species, trait) %>% summarise(mean_value = mean(value))

#sp_mean_all4 <- traits %>% filter(trait %in% c("leaf_area_cm2", "leaf_thickness_mm", "ldmc", "sla_cm2_g")) %>%
#                select(c(species, trait, value)) %>% group_by(species, trait) %>% summarise(mean_value = mean(value))

sp_mean_ctrl5 <- traits %>% filter(warming == "C" & trait %in% c("plant_height_cm", "leaf_area_cm2", "leaf_thickness_mm", "ldmc", "sla_cm2_g")) %>% select(c(species, trait, value)) %>% group_by(species, trait) %>% summarise(mean_value = mean(value))

#sp_mean_ctrl4 <- traits %>% filter(warming == "C" & trait %in% c("leaf_area_cm2", "leaf_thickness_mm", "ldmc", "sla_cm2_g")) %>%
#                 select(c(species, trait, value)) %>% group_by(species, trait) %>% summarise(mean_value = mean(value))

mat <- sp_mean_ctrl5 %>% pivot_wider(names_from = trait, values_from = mean_value)
mat[,2:6] <- scale(mat[,2:6])

dist_euc <- mat %>% column_to_rownames(var = "species")
dist_euc <- dist(dist_euc, method = "euclidean") # Compute distance matrix
hclusters <- hclust(dist_euc, method = "ward.D2") # Hierarchical clustering

fviz_dend(hclusters, cex = 0.8, k = 5, rect = TRUE, scale = "none", labels_track_height = 4.5, type = "rectangle") # print 600 x 450
groups_3 <- as.data.frame(cutree(hclusters, k = 3)) # 3 and 5 clusters makes sense
groups_5 <- as.data.frame(cutree(hclusters, k = 5))

sp_clust <- groups_3 %>% rownames_to_column(var = "species") %>% cbind(groups_5) %>% remove_rownames()
#sp_clust <- rename(sp_clust, clust3 = `cutree(hclusters, k = 3)`, clust5 = `cutree(hclusters, k = 5)`)
sp_clust$clust3 <- case_when(sp_clust$clust3 == 1 ~ "C", sp_clust$clust3 == 2 ~ "B", sp_clust$clust3 == 3 ~ "A")
sp_clust$clust5 <- case_when(sp_clust$clust5 == 1 ~ "C2", sp_clust$clust5 == 2 ~ "B1", sp_clust$clust5 == 3 ~ "B2",
                             sp_clust$clust5 == 4 ~ "C1", sp_clust$clust5 == 5 ~ "A")

#pairs.panels(mat[,2:6], lm = TRUE, smooth = FALSE, ellipse = FALSE, method = "pearson", hist.col = 4, stars = TRUE)
mat <- left_join(mat, sp_clust, by = "species")
colnames(mat) <- c("species", "LDMC", "LA", "LTH", "H", "SLA", "clust3", "clust5")
main_pcs <- prcomp(mat[,2:6], center = F, scale. = F)

#autoplot(main_pcs, loadings = TRUE, loadings.colour = 'blue', loadings.label = TRUE)
fviz_pca_biplot(main_pcs, habillage = mat$clust3, addEllipses = TRUE, geom = "point", repel = T,
                col.var="black", title = "Species clusters") + theme_classic()

rm(dist_euc, mat, hclusters, sp_mean_ctrl5, groups_3, groups_5)

```


# Computing Cohen's d
```{r}
# aggregated by site, block and experiment____________________________________________________________________________
traits1 <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(mean))
traits1 <- rename(traits1, mean_value = x)
traits1l <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(length))
traits1l <- rename(traits1l, n_obs = x)
traits1sd <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(var)) # default: sample not population variance
traits1sd$x <- sqrt(traits1sd$x)
traits1sd <- rename(traits1sd, sd = x)

# aggregated by site and experiment__________________________________________________________________________________
traits2 <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(mean))
traits2 <- rename(traits2, mean_value = x)
traits2l <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(length))
traits2l <- rename(traits2l, n_obs = x)
traits2sd <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(var)) # default: sample not population variance
traits2sd$x <- sqrt(traits2sd$x)
traits2sd <- rename(traits2sd, sd = x)

traits3 <- cbind(traits2, traits2l$n_obs, traits2sd$sd)
traits3 <- rename(traits3, n_obs = `traits2l$n_obs`, sd = `traits2sd$sd`)
traits3$ID <- paste(traits3$siteID, traits3$species, traits3$trait, sep = "_")
traits3C <- filter(traits3, warming == "C") # Control
traits3OTC <- filter(traits3, warming == "W") # Warming

traits3C <- traits3C %>% rename(C_mean = mean_value, C_n = n_obs, C_sd = sd) %>% select(-c(warming))
traits3OTC <- traits3OTC %>% rename(OTC_mean = mean_value, OTC_n = n_obs, OTC_sd = sd) %>%
  select(-c(siteID, species, warming, trait))

traits4 <- full_join(traits3C, traits3OTC, by = "ID")
traits4 <- select(traits4, -c(ID))
traits4 <- filter(traits4, !is.na(traits4$siteID) & !is.na(traits4$OTC_mean))
traits4 <- traits4 %>% mutate(mean_dif = C_mean - OTC_mean, n_dif = C_n - OTC_n, sd_dif = C_sd - OTC_sd)

traits4$pooled_SD <- NA
for(i in 1:nrow(traits4)) {
  traits4$pooled_SD[i] <- if(traits4$n_dif[i] == 0)
  {sqrt((traits4$C_sd[i]^2+traits4$OTC_sd[i]^2)/2)} # pooled sd for equal group sizes
  else {sqrt(((traits4$C_n[i] - 1) * traits4$C_sd[i]^2 + (traits4$OTC_n[i] - 1) * traits4$OTC_sd[i]^2) / (traits4$C_n[i] + traits4$OTC_n[i] - 2))} # pooled sd for unequal group sizes
  }

traits4$SES <- (traits4$OTC_mean - traits4$C_mean) / traits4$pooled_SD # Cohen's d: number of SDs between the two means:
 # mean(group a) - mean(group b) divided by pooled standard deviation.  https://en.wikiversity.org/wiki/Cohen%27s_d

traits4$PR <- (traits4$OTC_mean - traits4$C_mean) / traits4$C_mean # Relative Distance Plasticity Index: shows the factor by which the trait value in the OTC increased or decreased, in comparison to the control plot

traits4$trait <- case_when(traits4$trait == "leaf_area_cm2" ~ "LA", traits4$trait == "leaf_thickness_mm" ~ "LTH", traits4$trait == "sla_cm2_g" ~ "SLA", traits4$trait == "plant_height_cm" ~ "H", traits4$trait == "ldmc" ~ "LDMC", traits4$trait == "c_n" ~ "C:N", traits4$trait == "c_percent" ~ "LCC", traits4$trait == "d13c" ~ "δ13C", traits4$trait == "d15n" ~ "δ15N", traits4$trait == "n_percent" ~ "LNC")

traits4 <- traits4 %>% mutate(trait = factor(trait, levels = c("H", "LA", "LTH", "LDMC", "SLA", "LCC", "LNC", "C:N", "δ13C", "δ15N")))

#sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", 
                                                                       
traits_f <- traits4 %>% filter(!is.na(SES)) %>% group_by(trait) %>% mutate(trait_mean = mean(SES), trait_sd = sd(SES)) # trait table filtered
traits_f$outlier3 <- case_when(traits_f$SES <= traits_f$trait_mean - 3* traits_f$trait_sd ~ "low",
                               traits_f$SES >= traits_f$trait_mean + 3* traits_f$trait_sd ~ "high") # 6 outliers +- 3 sd away from the mean removed
traits_f <- traits_f %>% filter(is.na(outlier3)) %>% select(-c(trait_mean, trait_sd, outlier3))

rm(traits1, traits1l, traits1sd, traits2, traits2l, traits2sd, traits3, traits3C, traits3OTC, i)
```

# Sorting species by Ellenberg-type indicator values (Moisture) or MAT from Lynn et al.
```{r}
# Sources: https://onlinelibrary.wiley.com/doi/full/10.1111/jvs.13168
# https://floraveg.eu/download/

etiv <- readr::read_tsv("../Input data/Ellenberg_disturbance.txt", guess_max = Inf) # Ellenberg-type indicator values
#etiv$taxon_simpl <- str_replace_all(etiv$TaxonName, " aggr.", "")

classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)
classification$Type <- case_when(str_detect(classification$species, "Agrostis|Anthoxanthum|Carex|Festuca|Poa|Avenella|Deschampsia|Nardus") ~ "Graminoids", TRUE ~ "Forbs")

MAT <- readr::read_tsv("../Input data/MAT Lynn et al.txt")
MAT <- as.data.frame(MAT)
traits_MAT <- traits_f %>% ungroup() %>% left_join(MAT, by = "species")
traits_MAT <- traits_MAT %>% mutate(siteID = factor(siteID, levels = c("Ulvehaugen", "Gudmedalen", "Skjelingahaugen")))
traits_MAT <- filter(traits_MAT, !c(siteID == "Ulvehaugen" & trait == "δ13C"))
traits_MAT <- traits_MAT %>% left_join(classification, by = "species")
#sp_moisture <- traits_f %>% ungroup() %>% select(species) %>% unique() %>% left_join(etiv[,c(25,6)], by = c("species" = "taxon_simpl"))
# Scorzoneroides autumnalis instead of Leontodon autumnalis. Mismachted, but moisture == 5.5
#sp_moisture[sp_moisture$species == "Leontodon autumnalis", "Moisture"] <- "5.5" # X means species is indifferent to that factor

cor_plots <- ggplot(traits_MAT, aes(x = MAT_C, y = SES)) + geom_point(aes(color = Type)) +
  facet_wrap(~ trait, ncol = 4, scales = "free_x", labeller = label_parsed) +
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1), legend.position = "top") +
  labs(title = NULL, x = "Mean annual temperature [°C]", y = "Cohen's d") +
  geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
  #scale_color_manual(values = c("#c6dbef", "#6baed6", "#08519c")) +
  geom_smooth(aes(color = Type), method = "lm", se = TRUE, linetype = "solid") +  # Add regression line with confidence interval, alternative: no aes and color = "black"
  stat_poly_eq(aes(label = after_stat(paste(eq.label, p.value.label, sep = "*\", \"*")), color = Type),
    formula = y ~ x, parse = TRUE, size = 3) # Include p-value
# print 800 x 600
```

#Species trait tables
```{r}
#n_obs <- traits4 %>% filter(!is.na(SES)) %>% group_by(siteID, trait) %>% mutate(n_obs = n()) %>% sample_n(1) %>% select(siteID, trait, n_obs)

species_SES_table <- traits_f %>% group_by(species, trait) %>% mutate(mean_SES = var(SES)) %>% # change mean to var
  select(species, trait, mean_SES) %>% sample_n(1) %>%
  pivot_wider(names_from = trait, values_from = mean_SES)
species_SES_table$mean_overall <- rowMeans(abs(species_SES_table[,2:11]), na.rm = TRUE)

trait_SES_table <- traits_f %>% group_by(trait) %>% summarize(meanSES = mean(SES), absSES = mean(abs(SES)),
                                                           varSES = var(SES), nsamples = n())
cor.test(trait_SES_table$absSES, trait_SES_table$varSES, method = "pearson")

#_______________________________________________________________________________
sp_tables <- traits_f  %>% select(siteID, species, trait, SES) #%>% filter(trait != "C:N")

data_all_sites <- sp_tables %>% mutate(siteID = "overall") %>% group_by(species, trait) %>% mutate(SES = mean(SES)) %>% sample_n(1) %>% ungroup()
sp_tables <- sp_tables %>% bind_rows(data_all_sites)
sp_tables$precip <- case_when(sp_tables$siteID == "Ulvehaugen" ~ "low", sp_tables$siteID == "Gudmedalen" ~ "medium",
                                 sp_tables$siteID == "Skjelingahaugen" ~ "high", sp_tables$siteID == "overall" ~ "overall")
sp_tables <- sp_tables %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall"))) %>% select(-c(siteID))

#sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Veronica alpina", "Sibbaldia procumbens", "Salix herbacea", "Astragalus alpinus", "Carex bigelowii", "Viola biflora", "Saussurea alpina", "Thalictrum alpinum", "Poa alpina", "Alchemilla alpina", "Bistorta vivipara", "Carex vaginata", "Nardus stricta", "Campanula rotundifolia", "Anthoxanthum alpinum", "Agrostis capillaris", "Leontodon autumnalis"))) # SORTED BY MEAN ANNUAL GROWING TEMPERATURE FOR THE GEOGRAPHIC RANGE FROM LYNN

#sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", "Astragalus alpinus", "Bistorta vivipara", "Carex bigelowii", "Poa alpina", "Salix herbacea", "Saussurea alpina", "Sibbaldia procumbens", "Thalictrum alpinum", "Veronica alpina", "Viola biflora", "Agrostis capillaris", "Anthoxanthum alpinum", "Campanula rotundifolia", "Carex vaginata", "Leontodon autumnalis", "Nardus stricta"))) # GENERALIST V ALPINE

sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", "Astragalus alpinus", "Bistorta vivipara", "Campanula rotundifolia", "Leontodon autumnalis", "Salix herbacea", "Saussurea alpina", "Sibbaldia procumbens", "Thalictrum alpinum", "Veronica alpina", "Viola biflora", "Agrostis capillaris", "Anthoxanthum alpinum", "Carex bigelowii", "Carex vaginata", "Nardus stricta", "Poa alpina"))) # GRAMINOIDS V FORBS

#sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Agrostis capillaris", "Anthoxanthum alpinum", "Astragalus alpinus", "Campanula rotundifolia", "Leontodon autumnalis", "Veronica alpina", "Viola biflora", "Alchemilla alpina", "Poa alpina", "Salix herbacea", "Sibbaldia procumbens", "Thalictrum alpinum", "Bistorta vivipara", "Carex bigelowii", "Carex vaginata", "Nardus stricta", "Saussurea alpina"))) # GROUPS BASED ON CLUSTER ANALYSIS (3/5)

sp_tables <- sp_tables %>% ungroup() %>% complete(species, trait, precip, fill = list(SES = NA))

points_plot <- ggplot(sp_tables, aes(x = precip, y = species)) +
  geom_point(data = filter(sp_tables, !is.na(SES)), aes(size  = abs(SES), color = SES > 0)) +
  geom_point(data  = filter(sp_tables, is.na(SES)), aes(size = 1), shape = 45, color = "black") +
  scale_color_manual(values = c("red", "blue"), labels = c("negative", "positive")) +
  scale_size_continuous(range = c(0.5,6), breaks = c(0.1, 1, 2, 3)) + # c(1, 10)
  scale_y_discrete(limits = rev(levels(sp_tables$species))) + theme_classic() +
  labs(title = NULL, x = "Precipitation", y = NULL, size = "Standardized effect size [Cohen's d]", color = NULL) +
  geom_hline(aes(yintercept = 6.5), lty = 2, linewidth = 0.25) +
  facet_wrap(~ trait, ncol = 4) + # scales = "free"
  annotate("text", x = 4.3, y = 8.7, label = "Forbs 🡺", angle = 90, size = 4) + # y = 8.7, label = "Forbs 🡺"
  annotate("text", x = 4.3, y = 3.7, label = "Graminoids", angle = 90, size = 4) + # "🡸 Generalist" | y = 3.7, label = "Graminoids"
  annotate("rect", xmin = 3.5, xmax = 4.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.2) +
  theme(legend.position = "top", strip.text = element_text(size = 10, face = "bold"),
        axis.title = element_text(size = 12), panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        axis.text.y = element_text(face = "italic"))

# print 800 x 1000
# Helpful Unicode tables for arrows: https://en.wikipedia.org/wiki/Arrow_(symbol)

points_plot <- ggplot(sp_tables, aes(x = precip, y = species, size = abs(SES), color = SES > 0)) + geom_point() +
  scale_color_manual(values = c("red", "blue"), labels = c("negative", "positive")) +
  scale_size_continuous(range = c(0.5,6), breaks = c(0.1, 1, 2, 3)) + # c(1, 10)
  scale_y_discrete(limits = rev(levels(sp_tables$species))) + theme_classic() +
  labs(title = NULL, x = "Precipitation", y = NULL, size = "Standardized effect size [Cohen's d]", color = NULL) +
  geom_hline(yintercept = c(1.5, 10.5), lty = 1, linewidth = 0.25) +
  geom_hline(yintercept = c(5.5, 14.5), lty = 2, linewidth = 0.25) +  
  facet_wrap(~ trait, ncol = 4) + # scales = "free"
  annotate("text", x = 4.3, y = c(16, 12, 7, 3, 1), label = c("A1", "A2", "B1", "B2", "C"), angle = 90, size = 4) +
  annotate("rect", xmin = 3.5, xmax = 4.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.2) +
  theme(legend.position = "top", strip.text = element_text(size = 10, face = "bold"),
        axis.title = element_text(size = 12), panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
        axis.text.y = element_text(face = "italic"))

rm(sp_tables, data_all_sites, points_plot)
```

# Does Cmean influence d?
```{r}
traits_cor <- traits_f %>% mutate(siteID = factor(siteID, levels = c("Ulvehaugen", "Gudmedalen", "Skjelingahaugen")))

traits_cor <- traits_cor %>% mutate(trait = factor(trait,
              levels = c("H", "LA", "LTH", "LDMC", "SLA", "LCC", "LNC", "C:N", "δ13C", "δ15N"),
              labels = c(expression(paste("H [cm]")), expression(paste("LA [cm"^2*"]")), expression(paste("LTH [mm]")), expression(paste("LDMC [mg g"^-1*"]")), expression(paste("SLA [cm"^2*" g"^-1*"]")), expression(paste("LCC [%]")), expression(paste("LNC [%]")), expression(paste("C:N Ratio")), expression(paste("δ13C [‰]")), expression(paste("δ15N [‰]")))))

cor_plots <- ggplot(traits_cor, aes(x = C_mean, y = SES)) + geom_point(aes(color = siteID)) +
  facet_wrap(~ trait, ncol = 4, scales = "free_x", labeller = label_parsed) +
  theme_classic() +
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 1), legend.position = "top") +
  labs(title = NULL, x = "Control trait mean", y = "Cohen's d") +
  geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
  scale_color_manual(values = c("#c6dbef", "#6baed6", "#08519c")) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "solid") +  # Add regression line with confidence interval
  stat_poly_eq(
    aes(label = after_stat(paste(eq.label, p.value.label, sep = "*\", \"*"))),
    formula = y ~ x, parse = TRUE, size = 3) # Include p-value
# print 800 x 600

rm(traits_cor, cor_plots)
```


#  Testing for differences in variance between traits using f-tests
```{r}
trait_comp <- traits_f %>% mutate(trait = "overall") %>% rbind(traits_f)
site_comp <- traits_f %>% mutate(siteID = "overall") %>% rbind(traits_f)
species_comp <- traits_f %>% mutate(species = "overall") %>% rbind(traits_f)
Ulv <- site_comp %>% filter(siteID %in% c("overall", "Ulvehaugen"))
Gud <- site_comp %>% filter(siteID %in% c("overall", "Gudmedalen"))
Skj <- site_comp %>% filter(siteID %in% c("overall", "Skjelingahaugen"))

results <- data.frame(
  trait = character(),
  df_trait = integer(),
  df_overall = integer(),
  f_statistic = numeric(),
  p_value = numeric(),
  stringsAsFactors = FALSE)

# Loop through all traits except "overall"
for(t in unique(trait_comp$trait[trait_comp$trait != "overall"])) {
  ses_trait <- trait_comp$SES[trait_comp$trait == t]
  ses_overall <- trait_comp$SES[trait_comp$trait == "overall"]
  test <- var.test(ses_trait, ses_overall) # F-test for comparing variances
  
  results <- rbind(results, data.frame(
    trait = t,
    df_trait = test$parameter[1],
    df_overall = test$parameter[2],
    f_statistic = test$statistic,
    p_value = test$p.value))}


# Loop through all traits and compare between site and overall
for(t in unique(Skj$trait)) {
  ses_site <- Skj$SES[Skj$trait == t & Skj$siteID == "Skjelingahaugen"]
  ses_overall <- Skj$SES[Skj$trait == t & Skj$siteID == "overall"]
  test <- var.test(ses_site, ses_overall) # F-test for comparing variances
  
  results <- rbind(results, data.frame(
    trait = t,
    df_trait = test$parameter[1],
    df_overall = test$parameter[2],
    f_statistic = test$statistic,
    p_value = test$p.value))}

# Loop through species and compare species Cohen's d variance to overall variance
for(s in unique(species_comp$species[species_comp$species != "overall"])) {
  ses_single <- species_comp$SES[species_comp$species == s]
  ses_overall <- species_comp$SES[species_comp$species == "overall"]
  test <- var.test(ses_single, ses_overall) # F-test for comparing variances
  
  results <- rbind(results, data.frame(
    species = s,
    df_trait = test$parameter[1],
    df_overall = test$parameter[2],
    f_statistic = test$statistic,
    p_value = test$p.value))}

rm(trait_comp, site_comp, species_comp, Ulv, Gud, Skj, results, test, ses_overall, ses_traits, results, ses_site, s, t, ses_single, )
```


# Testing for differences using t-tests and f-tests
```{r}
classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)
classification$Type <- case_when(str_detect(classification$species, "Agrostis|Anthoxanthum|Carex|Festuca|Poa|Avenella|Deschampsia|Nardus") ~ "Graminoids", TRUE ~ "Forbs")

# comparison alpine vs generalist species and graminoids vs. Forbs
SES_compare <- traits_f %>% select(siteID, species, trait, SES) %>% left_join(classification, by = "species")
#SES_compare$SES <- abs(SES_compare$SES) # Optional. Depending if you want to compare actual or absolute SES values

#Checking t-test assumptions (normality and equal variances)
norm_test <- SES_compare %>% group_by(trait, as.factor(Type)) %>% summarise(p_value = shapiro.test(SES)$p.value) # no violations of normal distribution at p < 0.5
norm_plots <- ggplot(SES_compare, aes(sample = SES)) + geom_qq() + geom_qq_line() + facet_wrap(~ trait + Type) # qq-plot visual inspection
var_test <- SES_compare %>% group_by(trait) %>% summarise(p_value = var.test(SES ~ as.factor(Type))$p.value)
# unequal variances in graminoids and herbs for LA, Lth, D15N and LDMC. For these traits, report Welch’s t-test (var.equal = FALSE)

#Running t-tests
t_test_results <- SES_compare %>% do(t_test = t.test(SES ~ as.factor(Type), data = ., var.equal = FALSE)) %>% ungroup() # change var.equal

mean_test_results <- t_test_results %>% mutate(
                     t_statistic = sapply(t_test, function(x) x$statistic), # t-statistic
                     df = sapply(t_test, function(x) x$parameter[1]),
                     estimate1 = sapply(t_test, function(x) x$estimate[1]),
                     estimate2 = sapply(t_test, function(x) x$estimate[2]),
                     p_value = sapply(t_test, function(x) x$p.value)) %>%
    select(trait, t_statistic, df, estimate1, estimate2, p_value) 

var_test_results <- SES_compare %>% do(var_test = var.test(SES ~ factor(Type, levels = c("Forbs", "Graminoids")), data = .)) %>% ungroup() # alternatively: factor(alpine, levels = c(0, 1))
var_test_summary <- var_test_results %>% mutate(
    f_statistic = sapply(var_test, function(x) x$statistic), # f-statistic and ratio of variances are the same.
    df1 = sapply(var_test, function(x) x$parameter[1]),
    df2 = sapply(var_test, function(x) x$parameter[2]),
    p_value = sapply(var_test, function(x) x$p.value)) %>%
  select(trait, f_statistic, df1, df2, p_value)


#_______________________________________________________________________________

site_comp <- traits_f %>% mutate(comp1 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Gudmedalen" ~ "Gud"),
                                  comp2 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Skjelingahaugen" ~ "Skj"),
                                  comp3 = case_when(siteID == "Gudmedalen" ~ "Gud", siteID == "Skjelingahaugen" ~ "Skj"))

norm_test <- site_comp %>% group_by(trait, siteID) %>% summarise(p_value = shapiro.test(SES)$p.value) # non-normal distribution for H in Ulvehaugen and LDMC in Ulv and Skj
norm_plots <- ggplot(site_comp, aes(sample = SES)) + geom_qq() + geom_qq_line() + facet_wrap(~ trait + siteID) # qq-plot visual inspection

comp3 <- site_comp %>% select(-c(comp2, comp1)) %>% na.omit() %>% group_by(trait)
var_test <- comp3 %>% group_by(trait) %>% summarise(p_value = var.test(SES ~ as.factor(siteID))$p.value) # unequal variance only for D15N between Ulv:Skj / low:high

t_test_results <- comp1 %>% do(t_test = t.test(SES ~ as.factor(comp1), data = ., var.equal = F)) %>% ungroup()
w_test_results <- comp1 %>% do(w_test = wilcox.test(SES ~ as.factor(comp1), data = .)) %>% ungroup()

wil_tests <- comp3 %>% summarise(wilcox_test = list(wilcox.test(SES ~ as.factor(comp3))), .groups = "drop") %>%
  mutate(p_value = map_dbl(wilcox_test, ~ .x$p.value)) %>% select(-wilcox_test)

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value)
#test <- comp1 %>% group_by(trait, comp1) %>% summarize(mean = mean(trait_mean)) # shows trait means by group

print(p_values)

```


# Summarizing patterns
```{r}
classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)
classification$Type <- case_when(str_detect(classification$species, "Agrostis|Anthoxanthum|Carex|Festuca|Poa|Avenella|Deschampsia|Nardus") ~ "Graminoids", TRUE ~ "Forbs")

# species with most medium to high effect sizes, alpine vs. generalists
SES_lim <- traits_f %>% select(siteID, species, trait, SES) %>% group_by(species)
SES_lim <- SES_lim %>% summarize(total = n(), limit_1 = sum(abs(SES) >= 1), limit_08 = sum(abs(SES) >= 0.8), limit_05 = sum(abs(SES) >= 0.5))
SES_lim <- SES_lim %>% left_join(classification[,1:4], by = "species") %>% mutate(alpine = str_replace_all(alpine, c("1" = "Alpine", "0" = "Generalist")))

fun_type <- SES_lim %>% group_by(Type) %>% summarize(across(2:5, sum))
fun_type <- fun_type %>% mutate(limit_08 = limit_08 - limit_1, limit_05 = limit_05 - (limit_08 + limit_1),
                              total = total - (limit_05 + limit_08 + limit_1)) %>%
           pivot_longer(cols = 2:5, names_to = "Category", values_to = "Value") %>% ungroup() # changing counts so that each column contains only the surplus
fun_type$Category <- factor(fun_type$Category, levels = c("total", "limit_05", "limit_08", "limit_1"))
fun_type$perc <- case_when(fun_type$Type == "Forbs" ~ fun_type$Value/261 *100,
                           fun_type$Type == "Graminoids" ~ fun_type$Value/153 *100)

bar_plot <- ggplot(fun_type, aes(x = Type, y = Value, fill = Category)) +
  geom_bar(stat = "identity", width = 0.7, color = "black") + # or position = "dodge" # or without position and alpha, as stacked graph
  scale_fill_manual(values = c("white", "#cccccc", "#969696", "#636363"), labels = c("SES < 0.5", "SES \u2265 0.5", "SES \u2265 0.8", "SES \u2265 1")) +
  facet_wrap(~ Type, scales = "free", ncol = 2) +
  labs(title = NULL, x = "", y = "Number of effect sizes") +
  theme_classic() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(), text = element_text(size = 14)) +
  geom_text(aes(label = paste0(sprintf("%1.1f", perc), "%")), position = position_stack(vjust = 0.5))
# print 500 x 420

#SES_lim$fraction <- SES_lim$sum_SES05/SES_lim$total # the fraction is important because there are more alpine than generalist species

#histograms
hist_table <- traits_f %>% ungroup() %>% select(species, SES) %>% left_join(classification[,1:4], by = "species") %>%
  mutate(Group = str_replace_all(alpine, c("1" = "Alpine", "0" = "Generalist")))
hist_table$Type <- factor(hist_table$Type, levels = c("Forbs", "Graminoids"))

percentiles <- aggregate(SES ~ Type, data = hist_table, function(x) c(mean = mean(x), Q05 = quantile(x, 0.05), Q95 = quantile(x, 0.95)))
percentiles <- do.call(data.frame, percentiles) # Flatten the nested columns
colnames(percentiles) <- c("Type", "mean", "Q05", "Q95")

hist_plot <- ggplot(hist_table, aes(x = SES, fill = Type)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  geom_vline(data = percentiles, aes(xintercept = mean), linetype = "dashed", linewidth = 1, color = c("black", "red")) +
  geom_vline(data = percentiles, aes(xintercept = Q05, color = Type), linetype = "dotted", linewidth = 1, color = c("black", "red")) +
  geom_vline(data = percentiles, aes(xintercept = Q95, color = Type), linetype = "dotted", linewidth = 1, color = c("black", "red")) +
  scale_fill_manual(values = c("darkgrey", "red")) +
  scale_color_manual(values = c("darkgrey", "red")) +
  labs(title = NULL, x = "Cohen's d", y = "Number of effect sizes") +
  theme_classic() +
  theme(legend.position = "top", text = element_text(size = 14))

combined_plot <- plot_grid(hist_plot, bar_plot, labels = c("a", "b"), ncol = 2, align = "h", axis =  "tb", rel_widths = c(1,1)) # print 800 x 500
```

# Plotting SES values: Violin plots
```{r}
SES_sites <- traits_f %>% select(siteID, species, trait, SES)

SES_sites$precip <- case_when(SES_sites$siteID == "Ulvehaugen" ~ "low", SES_sites$siteID == "Gudmedalen" ~ "medium", SES_sites$siteID == "Skjelingahaugen" ~ "high")

data_all_sites <- SES_sites %>% mutate(precip = "overall")
SES_combined <- bind_rows(SES_sites, data_all_sites)
SES_combined <- SES_combined %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall")))

#Testing assumptions. If n > 30 t-test is not important
norm_test <- SES_combined %>% group_by(trait, precip) %>% summarise(p_value = shapiro.test(SES)$p.value) # H and LDMC not normally distributed -> Wilcoxon signed-rank test
norm_plots <- ggplot(SES_combined, aes(sample = SES)) + geom_qq() + geom_qq_line() + facet_wrap(~ trait + precip) # qq-plot visual inspection

# Are mean SES values significantly different from 0?
t_tests <- SES_combined %>% select(-c(siteID, species)) %>% group_by(precip, trait) %>%
  summarise(t_test = list(t.test(SES, mu = 0, var.equal = F)), .groups = "drop") %>%  # Perform t-test against 0
  mutate(estimate = map_dbl(t_test, ~ .x$estimate),  # Extract mean SES
         t_value = map_dbl(t_test, ~ .x$statistic),  # Extract t-statistic
         p_value = map_dbl(t_test, ~ .x$p.value)     # Extract p-value
  ) %>% select(-t_test)

t_tests2 <- SES_combined %>% select(-c(siteID, species)) %>% group_by(precip, trait) %>%
  summarise(wilcox_test = list(wilcox.test(SES, mu = 0)), .groups = "drop") %>%  # Perform Wilcoxon test against 0
  mutate(estimate = map_dbl(wilcox_test, ~ median(SES_combined$SES)),  # Extract median SES (since Wilcoxon is non-parametric)
         W_value = map_dbl(wilcox_test, ~ .x$statistic),  # Extract Wilcoxon test statistic (W)
         p_value = map_dbl(wilcox_test, ~ .x$p.value)     # Extract p-value
  ) %>% select(-wilcox_test)

SES_mean <- SES_combined %>% group_by(precip, trait) %>% summarize(mean_SES = mean(SES), var_SES = var(SES), .groups = "drop")
SES_summary <- left_join(SES_mean, t_tests[,c(1:2,5)], by = c("precip", "trait"))
SES_summary <- SES_summary %>% mutate(significance = case_when(p_value < 0.05 ~ "🞲", p_value < 0.1  ~ "+", TRUE ~ ""),
                                label_text = paste0(round(mean_SES, 2), " ", significance))

sites_comp <- SES_summary %>% filter(mean_SES > -0.8) %>% group_by(precip) %>%
              summarise(mean_abs_SES = mean(abs(mean_SES)), mean_var = mean(var_SES)) # overall sites comparison

violin_plot <- ggplot(SES_combined, aes(x = precip, y = SES, fill = precip)) +
  geom_half_violin(side = "l", trim = TRUE, color = NA) +
  geom_half_point(side = "r", position = position_jitter(width = 0), alpha = 0.5, shape = 16) +
  geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
  geom_text(data = SES_summary, aes(x = precip, y = label_text, label = label_text), y = 1.9, vjust = -1, size = 3.5) +
  geom_point(stat = "summary", fun = "mean", size = 3, shape = 18) + 
  geom_errorbar(stat = "summary", fun.data = "mean_cl_normal", fun.args = list(mult = qnorm(0.975)),  width = 0, linewidth = 1) + # 
  # mean_se standard error, mean_cl_normal confidence intervals, mean_sdl standard deviation
  #before it was mean_se (standard error) and fun.args = list(mult = 1.96), that is different from actual confidence interval
  facet_wrap(~ trait, scales = "free", ncol = 2) + # Facet by trait
  scale_fill_manual(values = c("#c6dbef", "#6baed6", "#2171b5", "grey")) +
  theme_classic() +
  labs(title = NULL, x = "Precipitation", y = "Standardized effect size [Cohen's d]") +
  theme(legend.position = "none", strip.text = element_text(size = 10, face = "bold"), axis.title = element_text(size = 12)) +
  ylim(-2.62, 2.62) # otherwise ylim(-5,5)

# print 800 x 1000
rm(SES_sites, data_all_sites, SES_combined, SES_summary, violin_plot, t_tests)
#_______________________________________________________________________________ violin plots for all traits and across sites
#multi_bp <- ggplot(SES_sites, aes(x = trait, y = SES, group = trait)) + geom_violin(aes(fill = trait), trim = T) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) + stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
#               colour = "black") + ylim(-2.5,2.5) + geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.1)
# + geom_boxplot(aes(fill = trait), outlier.alpha = 0)

#_______________________________________________________________________________ violin plots for all traits and across sites but with mean values for species
#SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(2,3)], FUN = mean)
#SES_sites <- SES_sites %>% rename(`mean SES` = x)

#multi_bp <- ggplot(SES_sites, aes(x = trait, y = `mean SES`, group = trait)) +
#  geom_boxplot(aes(fill = trait), outlier.alpha = 0) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
#  geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.5) + ylim(-2.5,2)
```

# Functional differences between sites (trait means)
```{r}
site_comp <- traits %>% filter(warming == "C") %>% group_by(siteID, species, trait) %>%
             summarize(trait_mean = mean(value)) %>% ungroup() # site comparisons. 23 trait measurements missing.

site_comp$trait <- case_when(site_comp$trait == "leaf_area_cm2" ~ "LA", site_comp$trait == "leaf_thickness_mm" ~ "LTH", site_comp$trait == "sla_cm2_g" ~ "SLA", site_comp$trait == "plant_height_cm" ~ "H", site_comp$trait == "ldmc" ~ "LDMC", site_comp$trait == "c_n" ~ "C:N", site_comp$trait == "c_percent" ~ "LCC", site_comp$trait == "d13c" ~ "δ13C", site_comp$trait == "d15n" ~ "δ15N", site_comp$trait == "n_percent" ~ "LNC")

site_comp <- site_comp %>% mutate(trait = factor(trait,
              levels = c("H", "LA", "LTH", "LDMC", "SLA", "LCC", "LNC", "C:N", "δ13C", "δ15N"),
              labels = c(expression(paste("H [cm]")), expression(paste("LA [cm"^2*"]")), expression(paste("LTH [mm]")), expression(paste("LDMC [mg g"^-1*"]")), expression(paste("SLA [cm"^2*" g"^-1*"]")), expression(paste("LCC [%]")), expression(paste("LNC [%]")), expression(paste("C:N Ratio")), expression(paste("δ13C [‰]")), expression(paste("δ15N [‰]")))))

site_comp <- site_comp %>% group_by(species, trait) %>% mutate(Freq = n()) %>% ungroup()
site_comp <- site_comp %>% filter(Freq == 3) %>% select(-c(Freq)) # filtering out incomplete trait measurements (not in all 3 sites)
test <- as.data.frame(table(site_comp$trait))

site_comp$precip <- case_when(site_comp$siteID == "Ulvehaugen" ~ "low", site_comp$siteID == "Gudmedalen" ~ "medium", site_comp$siteID == "Skjelingahaugen" ~ "high")

data_all_sites <- site_comp %>% mutate(precip = "overall")
data_combined <- bind_rows(site_comp, data_all_sites)
data_combined <- data_combined %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall")))

mean_across <- data_combined %>% group_by(precip, trait) %>% summarize(overall_mean = mean(trait_mean), .groups = "drop")

violin_plot <- ggplot(data_combined, aes(x = precip, y = trait_mean, fill = precip)) +
  geom_half_violin(side = "l", trim = TRUE, color = NA) +
  geom_half_point(side = "r", position = position_jitter(width = 0), alpha = 0.5, shape = 16) +
  geom_hline(data = filter(mean_across, precip == "overall"), aes(yintercept = overall_mean), lty = 2, linewidth = 0.25) +
  geom_point(stat = "summary", fun = "mean", size = 3, shape = 18) + 
  geom_errorbar(stat = "summary", fun.data = "mean_se", fun.args = list(mult = 1.96), width = 0, linewidth = 1) +
  facet_wrap(~ trait, scales = "free", ncol = 2, labeller = label_parsed) + # Facet by trait
  scale_fill_manual(values = c("#c6dbef", "#6baed6", "#2171b5", "grey")) +
  theme_classic() +
  labs(title = NULL, x = "Precipitation", y = "Trait means") +
  theme(legend.position = "none", strip.text = element_text(size = 10, face = "bold"), axis.title = element_text(size = 12))
  #ylim(-2.62, 2.62) # otherwise ylim(-5,5)

# print 800 x 1000

# Assumption testing first
norm_test <- site_comp %>% group_by(trait, precip) %>% summarise(p_value = shapiro.test(trait_mean)$p.value) # Many non-normally distributed
norm_plots <- ggplot(site_comp, aes(sample = trait_mean)) + geom_qq() + geom_qq_line() + facet_wrap(~ trait + precip, scales = "free")

site_comp <- site_comp %>% mutate(comp1 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Gudmedalen" ~ "Gud"),
                                  comp2 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Skjelingahaugen" ~ "Skj"),
                                  comp3 = case_when(siteID == "Gudmedalen" ~ "Gud", siteID == "Skjelingahaugen" ~ "Skj"))

comp3 <- site_comp %>% select(-c(comp2, comp1)) %>% na.omit() %>% group_by(trait)
var_test <- comp3 %>% group_by(trait) %>% summarise(p_value = leveneTest(trait_mean ~ as.factor(comp3))$"Pr(>F)"[1]) # non equal variance for SLA between Gud:Skj Medium:high

t_test_results <- comp3 %>% do(t_test = t.test(trait_mean ~ as.factor(comp3), data = ., var.equal = T)) %>% ungroup()

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value)

wil_tests <- comp3 %>% summarise(wilcox_test = list(wilcox.test(trait_mean ~ as.factor(comp3))), .groups = "drop") %>%
  mutate(p_value = map_dbl(wilcox_test, ~ .x$p.value)) %>% select(-wilcox_test)

test <- comp1 %>% group_by(trait, comp1) %>% summarize(mean = mean(trait_mean)) # shows trait means by group

print(p_values)
# Significant differences: Ulv Gud only D13C, p = 0.05397769
# Ulv Skj only LCC p = 0.01907241	
# Gud Skj H p = 0.00504747
rm(mean_across, data_combined, data_all_sites, test)
```

# Plotting SES values
```{r}
SES_sites <- traits4 %>% select(c(1:3,5,8,14)) %>% na.omit()

SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(1,3)], FUN = mean)
SES_sites <- SES_sites %>% rename(`mean SES` = x)
SES_sites$level <- case_when(SES_sites$`mean SES` < 0 ~ "negative", SES_sites$`mean SES` > 0 ~ "positive")

test <- SES_sites %>% group_by(trait) %>% mutate(mean_trait = mean(`mean SES`)) %>% sample_n(1) %>% select(c(trait, mean_trait))

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Ulvehaugen", "Gudmedalen", "Skjelingahaugen"))
SES_sites$trait <- factor(SES_sites$trait, levels = c("LCC", "LNC", "C:N", "δ13C", "δ15N", "H", "LA", "LDMC", "LTH", "SLA"))

SES_plot <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, shape = level)) +  
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 16)) +
  geom_hline(yintercept = 0, lty = 2, size = 0.25) +
  coord_flip() +
  xlab("") + ylab("Absolute Cohen's d") +
  theme_bw() +
  guides(colour = "legend", shape = "none") +
  facet_grid(. ~ trait) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.position= "top",
        legend.text = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.text.x = element_text(angle=45, vjust=.5, size = 16),
        axis.text.y = element_text(vjust=.5, size = 16),
        strip.text = element_text(size = 16, face = "bold"))

# print 1200 x 400

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Skjelingahaugen", "Gudmedalen", "Ulvehaugen"))

SES_plot2 <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, group = trait)) +
  geom_line(aes(color = trait), linewidth = 1, alpha = 0.5) +
  geom_point(aes(color = trait), size = 2) +
  theme_classic() + xlab("") + ylab("Absolute Cohen's d") +
  theme(axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14, face = "bold"))
# print 600 x 400
```

# Species specific plasticity and succeptibility to warming
```{r}
# Species without paired observations (inside and outside OTC) are omitted!!
distribution <- readr::read_tsv("../Input data/species classifications.txt", guess_max = Inf)
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)

traits_scaled <- traits %>% as.data.frame() %>% select(species, trait, value)
traits_scaled <- traits_scaled %>% semi_join(filter(traits4, !is.na(SES)), by = "species") # remove species without SES values
traits_scaled <- traits_scaled %>% group_by(trait) %>% mutate(scaled_values = scale(value, center = T, scale = T)) %>% ungroup()

species_sd <- aggregate(traits_scaled$scaled_values, by = traits_scaled[,1:2], FUN = na.omit(var))
species_sd$V1 <- sqrt(species_sd$V1)
species_sd <- rename(species_sd, sd = V1)
species_sd <- species_sd %>% group_by(species) %>% summarise(mean_sd = mean(sd, na.rm = T))

species_n <- raw_traits %>% group_by(ID) %>% select(c(species, ID)) %>% slice_sample(n = 1)
species_n <- as.data.frame(table(species_n$species))
species_n <- rename(species_n, species = Var1)

mean_abs_SES <- traits4 %>% select(species, SES) %>% na.omit() %>% mutate(SES = abs(SES)) # mean absolute SES per species
mean_abs_SES <- mean_abs_SES %>% group_by(species) %>% summarise(mean_SES = mean(SES, na.rm = T)) # susceptibility to warming

sgnf_SES <- traits4 %>% filter(SES >= 1 | SES <= -1) %>% group_by(species) %>% summarise(sgnf_SES = n())

species_sd <- species_sd %>% left_join(species_n, by = "species") %>% left_join(distribution, by = "species") %>% left_join(mean_abs_SES, by = "species") %>% left_join(sgnf_SES, by = "species")

rm(traits_scaled, species_n, distribution, raw_traits, mean_abs_SES, sgnf_SES)

```

# DEPRECTAED
```{r}
# δ13c only has negative values while δ15N has positive and negative values
# Somehow for δ15N, values range around 0 so relative sd makes no sense as mean = 0 and sd = 1 ..
# Instead, use e.g. MAD mean absolute deviation. 1/n * sum(abs(x-mean)). That doesnt solve the problem. The problem is that traits have different units of measurement. To be able to compare variation between traits, I divide sd by mean which is not possible for δ15N. Instead, scale the traits seperately (?)
# Computation of Cohen's d is not affected by values ranging around 0

species_mad <- aggregate(traits$value, by = traits[,4:5],
                         FUN = function(x) ie2misc::madstat(x))
species_sd <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(var))
species_sd$x <- sqrt(species_sd$x)
species_sd <- rename(species_sd, sd = x)
species_mean <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(mean))

species_abs_SES <- traits4 %>% na.omit() %>% group_by(species) %>% summarise(mean_SES = mean(abs(SES)))

species_sd <- cbind(species_sd, species_mean[,3])
species_sd <- rename(species_sd, mean = `species_mean[, 3]`)
species_sd <- species_sd %>% mutate(rel_sd = sd / mean) #%>% select(-c(sd, mean))


rm(species_mean, species_abs_SES)
```

# plotting relationship between trait plasticity and species type
```{r}
p1 <- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_sd)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1), limits = c(0.4, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean sd per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# plotting relationship between susceptibility to warming and species type
```{r}
p2<- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_SES)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8), limits = c(0, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean absolute SES per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# t.tests
```{r}
all_cmb <- traits %>% select(-c(blockID, warming, value)) %>% group_by(siteID, species, trait) %>%
                      slice_sample(n = 1) # all combinations of sites, species and traits

out <- list() #output is list of p-values
for(i in 1:nrow(all_cmb)){ 
  tryCatch({
  cmb <- all_cmb[i,1:3]
  subset <- filter(traits,  siteID == paste(cmb[1,1]) & species == paste(cmb[1,2]) & trait == paste(cmb[1,3]))
  t_res <- t.test(subset$value ~ subset$warming)
  out[[i]]  <- paste(t_res$p.value, i)}, error = function(e){})
} # in every iteration I filter for one species, trait and site, output is list of p-values

out <- out[lapply(out, length) > 0]
t_results <- out %>% as.data.frame() %>% t() %>% as.data.frame()
t_results <- t_results %>% separate_wider_delim(V1, delim = " ", names = c("p-value", "iteration"))

all_cmb <- all_cmb %>% rownames_to_column(var = "iteration") %>% left_join(t_results, by = "iteration")
sign_cmb <- filter(all_cmb, `p-value` < 0.05)
```