---
title: "Standardized Effect Size"
author: "Joshua"
date: "2023-10-13"
output: html_document
---

# Packages
```{r echo = FALSE, print = FALSE, message = FALSE}
library("tidyverse")
library("ie2misc") # madstat mean absolute deviation
library("ggplot2")
library("gghalves")
```

# Re-arranging data frame and computing Cohen's d
```{r}
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)
chem_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_chemical_traits_2022.txt", guess_max = Inf)

chem_traits <- chem_traits %>% group_by(ID_merged, trait) %>% sample_n(1) 
chem_traits <- chem_traits %>% ungroup() %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("c_percent", "n_percent", "c_n", "d15n", "d13c")) # no sample removed, but trait phosphorus percentage removed because of missing data

traits <- raw_traits %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("ldmc", "leaf_area_cm2", "leaf_thickness_mm", "plant_height_cm", "sla_cm2_g")) # one sample removed: DLL3549
traits <- rbind(traits, chem_traits)

selected_sp <- traits %>% select(siteID, warming, species) %>% unique() %>% group_by(species) %>% mutate(Freq = n()) %>%
               filter(Freq >= 4 & species != "Achillea millefolium") # filtering species we have samples for in C and W for each site. n = 13. 2 sites n = 17. Not included is Achillea millefolium because it has warming samples only in Gud
selected_sp <- unique(selected_sp$species)
traits <- traits %>% filter(species %in% selected_sp) # trait set with only 17 selected species. xx.x % of data omitted
rm(test, chem_traits, raw_traits, selected_sp)

# aggregated by site, block and experiment____________________________________________________________________________
traits1 <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(mean))
traits1 <- rename(traits1, mean_value = x)
traits1l <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(length))
traits1l <- rename(traits1l, n_obs = x)
traits1sd <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(var)) # default: sample not population variance
traits1sd$x <- sqrt(traits1sd$x)
traits1sd <- rename(traits1sd, sd = x)

# aggregated by site and experiment__________________________________________________________________________________
traits2 <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(mean))
traits2 <- rename(traits2, mean_value = x)
traits2l <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(length))
traits2l <- rename(traits2l, n_obs = x)
traits2sd <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(var)) # default: sample not population variance
traits2sd$x <- sqrt(traits2sd$x)
traits2sd <- rename(traits2sd, sd = x)

traits3 <- cbind(traits2, traits2l$n_obs, traits2sd$sd)
traits3 <- rename(traits3, n_obs = `traits2l$n_obs`, sd = `traits2sd$sd`)
traits3$ID <- paste(traits3$siteID, traits3$species, traits3$trait, sep = "_")
traits3C <- filter(traits3, warming == "C") # Control
traits3OTC <- filter(traits3, warming == "W") # Warming

traits3C <- traits3C %>% rename(C_mean = mean_value, C_n = n_obs, C_sd = sd) %>% select(-c(warming))
traits3OTC <- traits3OTC %>% rename(OTC_mean = mean_value, OTC_n = n_obs, OTC_sd = sd) %>%
  select(-c(siteID, species, warming, trait))

traits4 <- full_join(traits3C, traits3OTC, by = "ID")
traits4 <- select(traits4, -c(ID))
traits4 <- filter(traits4, !is.na(traits4$siteID) & !is.na(traits4$OTC_mean))
traits4 <- traits4 %>% mutate(mean_dif = C_mean - OTC_mean, n_dif = C_n - OTC_n, sd_dif = C_sd - OTC_sd)

traits4$pooled_SD <- NA
for(i in 1:nrow(traits4)) {
  traits4$pooled_SD[i] <- if(traits4$n_dif[i] == 0)
  {sqrt((traits4$C_sd[i]^2+traits4$OTC_sd[i]^2)/2)} # pooled sd for equal group sizes
  else {sqrt(((traits4$C_n[i] - 1) * traits4$C_sd[i]^2 + (traits4$OTC_n[i] - 1) * traits4$OTC_sd[i]^2) / (traits4$C_n[i] + traits4$OTC_n[i] - 2))} # pooled sd for unequal group sizes
  }

traits4$SES <- (traits4$OTC_mean - traits4$C_mean) / traits4$pooled_SD # Cohen's d: number of SDs between the two means:
 # mean(group a) - mean(group b) divided by pooled standard deviation.  https://en.wikiversity.org/wiki/Cohen%27s_d

traits4$PR <- (traits4$OTC_mean - traits4$C_mean) / traits4$C_mean # Relative Distance Plasticity Index: shows the factor by which the trait value in the OTC increased or decreased, in comparison to the control plot

traits4$trait <- case_when(traits4$trait == "leaf_area_cm2" ~ "LA", traits4$trait == "leaf_thickness_mm" ~ "LTH", traits4$trait == "sla_cm2_g" ~ "SLA", traits4$trait == "plant_height_cm" ~ "H", traits4$trait == "ldmc" ~ "LDMC", traits4$trait == "c_n" ~ "C/N", traits4$trait == "c_percent" ~ "C %", traits4$trait == "d13c" ~ "D13C", traits4$trait == "d15n" ~ "D15N", traits4$trait == "n_percent" ~ "N %")

rm(traits1, traits1l, traits1sd, traits2, traits2l, traits2sd, traits3, traits3C, traits3OTC, i)
```

#Species trait tables
```{r}
#n_obs <- traits4 %>% filter(!is.na(SES)) %>% group_by(siteID, trait) %>% mutate(n_obs = n()) %>% sample_n(1) %>% select(siteID, trait, n_obs)

traits_f <- traits4 %>% filter(!is.na(SES)) %>% group_by(trait) %>% mutate(trait_mean = mean(SES), trait_sd = sd(SES)) # trait table filtered
traits_f$outlier3 <- case_when(traits_f$SES <= traits_f$trait_mean - 3* traits_f$trait_sd ~ "low",
                               traits_f$SES >= traits_f$trait_mean + 3* traits_f$trait_sd ~ "high") # 6 outliers +- 3 sd away from the mean removed
traits_f <- traits_f %>% filter(is.na(outlier3)) %>% select(-c(trait_mean, trait_sd, outlier3))

species_SES_table <- traits_f %>% group_by(species, trait) %>% mutate(mean_SES = mean(abs(SES))) %>%
  select(species, trait, mean_SES) %>% sample_n(1) %>%
  pivot_wider(names_from = trait, values_from = mean_SES)
species_SES_table$mean_overall <- rowMeans(abs(species_SES_table[,2:11]), na.rm = TRUE)

trait_SES_table <- traits_f  %>% group_by(trait) %>% mutate(meanSES = mean(SES), absSES = mean(abs(SES)), nsamples = n()) %>%
                   sample_n(1) %>% ungroup() %>% select(c(trait, meanSES, absSES, nsamples))

sp_tables <- traits_f  %>% select(siteID, species, trait, SES) #%>% filter(trait != "C/N")

data_all_sites <- sp_tables %>% mutate(siteID = "overall") %>% group_by(species, trait) %>% mutate(SES = mean(SES)) %>% sample_n(1) %>% ungroup()
sp_tables <- sp_tables %>% bind_rows(data_all_sites)
sp_tables$precip <- case_when(sp_tables$siteID == "Ulvehaugen" ~ "1315", sp_tables$siteID == "Gudmedalen" ~ "2118",
                                 sp_tables$siteID == "Skjelingahaugen" ~ "3601", sp_tables$siteID == "overall" ~ "overall")
sp_tables <- sp_tables %>% mutate(precip = factor(precip, levels = c("1315", "2118", "3601", "overall"))) %>% select(-c(siteID))
sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", "Astragalus alpinus", "Bistorta vivipara", "Carex bigelowii", "Poa alpina", "Salix herbacea", "Saussurea alpina", "Sibbaldia procumbens", "Thalictrum alpinum", "Veronica alpina", "Viola biflora", "Agrostis capillaris", "Anthoxanthum odoratum", "Campanula rotundifolia", "Carex vaginata", "Leontodon autumnalis", "Nardus stricta")))

table_plots <- ggplot(sp_tables, aes(x = precip, y = species, size = abs(SES), color = SES > 0)) + geom_point() +
  scale_color_manual(values = c("red", "blue"), labels = c("negative", "positive")) +
  scale_size_continuous(range = c(0.5,8), breaks = c(0.1, 1, 2, 3)) + theme_classic() + # c(1, 10)
  scale_y_discrete(limits = rev(levels(sp_tables$species))) +
  labs(title = NULL, x = "Precipitation [mm]", y = NULL, size = "Standardized effect size [Cohen's d]", color = NULL) + theme(legend.position = "top") +
  geom_hline(aes(yintercept = 6.5), lty = 2, linewidth = 0.25) +
  facet_wrap(~ trait, scales = "free", ncol = 5) + annotate("text", x = 4.3, y = 8, label = "alpine", angle = 90, size = 4) + # before: x = 4.4, y = 7.5
  annotate("text", x = 4.3, y = 2.5, label = "generalist", angle = 90, size = 4) # before: x = 4.4, y = 2

# print 1600 x 1000
rm(sp_tables, data_all_sites, species_SES_table, trait_SES_table, table_plots)
```

# Summarizing patterns
```{r}
classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)

patterns <- traits_f %>% select(siteID, species, trait, SES)
patterns$effect <- case_when(patterns$SES >= 0 ~ 1, patterns$SES < 0 ~ -10)
patterns <- patterns %>% group_by(species, trait) %>% summarize(mean_effect = sum(effect), .groups = "drop")
patterns <- as.data.frame(table(patterns$mean_effect))
# index: 1,2 and 3: all increase. -30, -20, -10 all decrease. -19, -9, -8 flip
# results: all increase: x43, all decrease: x33, flip: 93
#how many times do we have increase, decrease or flip.

# species with most medium to high effect sizes, alpine vs. generalists
SES_lim <- traits_f %>% select(siteID, species, trait, SES) %>% group_by(species)
SES_lim <- SES_lim %>% summarize(total = n(), limit_1 = sum(abs(SES) >= 1), limit_08 = sum(abs(SES) >= 0.8), limit_05 = sum(abs(SES) >= 0.5))
SES_lim <- SES_lim %>% left_join(classification[,1:2], by = "species") %>% mutate(alpine = str_replace_all(alpine, c("1" = "alpine", "0" = "generalist")))

alp_gen <- SES_lim %>% group_by(alpine) %>% summarize(across(2:5, sum)) %>%
           pivot_longer(cols = 2:5, names_to = "Category", values_to = "Value")
alp_gen <- alp_gen %>% ungroup() %>% mutate(Category = factor(Category, levels = c("total", "limit_1", "limit_08", "limit_05")))
# alp_gen$Category <- factor(alp_gen$Category, levels = c("SES1", "SES08", "SES05", "all"))

bar_plot <- ggplot(alp_gen, aes(x = alpine, y = Value, fill = Category)) +
  geom_bar(stat = "identity", position = "identity", width = 0.7, color = "black") + # or position = "dodge" # or without position and alpha, as stacked graph # 
  scale_fill_manual(values = c("black", "darkgrey", "lightgrey", "white"), labels = c("SES1", "SES08", "SES05", "all")) +
  facet_wrap(~ alpine, scales = "free", ncol = 2) +
  labs(title = NULL,
       x = NULL,
       y = "Sum of SES values") +
  theme_classic() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())

SES_lim$fraction <- SES_lim$sum_SES05/SES_lim$total # the fraction is important because there are more alpine than generalist species

t.test(sum_SES05 ~ alpine, data = SES_lim) # neither sum nor fraction are significantly different between alpine and generalist species

#histograms
alpine <- traits_f %>% select(siteID, species, trait, SES) %>% left_join(classification[,1:2], by = "species") %>% filter(alpine == 1)
hist_alp <- hist(alpine$SES, breaks = 20) # print 600 x 400

generalist <- traits_f %>% select(siteID, species, trait, SES) %>% left_join(classification[,1:2], by = "species") %>% filter(alpine == 0)
hist_gen <- hist(generalist$SES) # print 600 x 400

# stacked bar plots


# comparison alpine vs generalist species
SES_compare <- traits_f %>% select(siteID, species, trait, SES) %>% left_join(classification, by = "species")
SES_compare$SES <- abs(SES_compare$SES)
t_test_results <- SES_compare %>% do(t_test = t.test(SES ~ alpine, data = .)) %>% ungroup()

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value)

print(p_values)

```

# Plotting SES values: Boxplots
```{r}
SES_sites <- traits_f %>% select(siteID, species, trait, SES)

SES_sites$precip <- case_when(SES_sites$siteID == "Ulvehaugen" ~ "1315", SES_sites$siteID == "Gudmedalen" ~ "2118", SES_sites$siteID == "Skjelingahaugen" ~ "3601")

data_all_sites <- SES_sites %>% mutate(precip = "overall")
SES_combined <- bind_rows(SES_sites, data_all_sites)
SES_combined <- SES_combined %>% mutate(precip = factor(precip, levels = c("1315", "2118", "3601", "overall")))

SES_mean <- SES_combined %>% group_by(precip, trait) %>% summarize(mean_SES = mean(SES), .groups = "drop")

panel_plots <- ggplot(SES_combined, aes(x = precip, y = SES, fill = precip)) +
  geom_half_violin(side = "l", trim = TRUE, colour = NA) +
  geom_half_point(side = "r", position = position_jitter(width = 0), alpha = 0.5, shape = 16) +
  geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
  geom_text(data = SES_mean, aes(x = precip, y = mean_SES, label = round(mean_SES, 2)), y = 2,
    vjust = -1, # Adjust vertical position
    size = 3.5) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "black", linewidth = 1) +
  facet_wrap(~ trait, scales = "free", ncol = 2) + # Facet by trait
  scale_fill_brewer(palette = "Set2") + # Optional color palette
  theme_classic() +
  labs(title = NULL, x = "Precipitation [mm]", y = "Standardized effect size [Cohen's d]") +
  theme(legend.position = "none", strip.text = element_text(size = 10, face = "bold"), axis.title = element_text(size = 12)) +
  ylim(-2.62, 2.62) # otherwise ylim(-5,5)

# print 1000 x 1200

#_______________________________________________________________________________ violin plots for all traits and across sites
#multi_bp <- ggplot(SES_sites, aes(x = trait, y = SES, group = trait)) + geom_violin(aes(fill = trait), trim = T) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) + stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
#               colour = "black") + ylim(-2.5,2.5) + geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.1)
# + geom_boxplot(aes(fill = trait), outlier.alpha = 0)

#_______________________________________________________________________________ violin plots for all traits and across sites but with mean values for species
#SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(2,3)], FUN = mean)
#SES_sites <- SES_sites %>% rename(`mean SES` = x)

#multi_bp <- ggplot(SES_sites, aes(x = trait, y = `mean SES`, group = trait)) +
#  geom_boxplot(aes(fill = trait), outlier.alpha = 0) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
#  geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.5) + ylim(-2.5,2)
```

# Plotting SES values
```{r}
SES_sites <- traits4 %>% select(c(1:3,5,8,14)) %>% na.omit()

SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(1,3)], FUN = mean)
SES_sites <- SES_sites %>% rename(`mean SES` = x)
SES_sites$level <- case_when(SES_sites$`mean SES` < 0 ~ "negative", SES_sites$`mean SES` > 0 ~ "positive")

test <- SES_sites %>% group_by(trait) %>% mutate(mean_trait = mean(`mean SES`)) %>% sample_n(1) %>% select(c(trait, mean_trait))

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Ulvehaugen", "Gudmedalen", "Skjelingahaugen"))
SES_sites$trait <- factor(SES_sites$trait, levels = c("C %", "N %", "C/N", "D13C", "D15N", "H", "LA", "LDMC", "LTH", "SLA"))

SES_plot <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, shape = level)) +  
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 16)) +
  geom_hline(yintercept = 0, lty = 2, size = 0.25) +
  coord_flip() +
  xlab("") + ylab("Absolute Cohen's d") +
  theme_bw() +
  guides(colour = "legend", shape = "none") +
  facet_grid(. ~ trait) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.position= "top",
        legend.text = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.text.x = element_text(angle=45, vjust=.5, size = 16),
        axis.text.y = element_text(vjust=.5, size = 16),
        strip.text = element_text(size = 16, face = "bold"))

# print 1200 x 400

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Skjelingahaugen", "Gudmedalen", "Ulvehaugen"))

SES_plot2 <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, group = trait)) +
  geom_line(aes(color = trait), linewidth = 1, alpha = 0.5) +
  geom_point(aes(color = trait), size = 2) +
  theme_classic() + xlab("") + ylab("Absolute Cohen's d") +
  theme(axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14, face = "bold"))
# print 600 x 400
```

# Species specific plasticity and succeptibility to warming
```{r}
# Species without paired observations (inside and outside OTC) are omitted!!
distribution <- readr::read_tsv("../Input data/species classifications.txt", guess_max = Inf)
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)

traits_scaled <- traits %>% as.data.frame() %>% select(species, trait, value)
traits_scaled <- traits_scaled %>% semi_join(filter(traits4, !is.na(SES)), by = "species") # remove species without SES values
traits_scaled <- traits_scaled %>% group_by(trait) %>% mutate(scaled_values = scale(value, center = T, scale = T)) %>% ungroup()

species_sd <- aggregate(traits_scaled$scaled_values, by = traits_scaled[,1:2], FUN = na.omit(var))
species_sd$V1 <- sqrt(species_sd$V1)
species_sd <- rename(species_sd, sd = V1)
species_sd <- species_sd %>% group_by(species) %>% summarise(mean_sd = mean(sd, na.rm = T))

species_n <- raw_traits %>% group_by(ID) %>% select(c(species, ID)) %>% slice_sample(n = 1)
species_n <- as.data.frame(table(species_n$species))
species_n <- rename(species_n, species = Var1)

mean_abs_SES <- traits4 %>% select(species, SES) %>% na.omit() %>% mutate(SES = abs(SES)) # mean absolute SES per species
mean_abs_SES <- mean_abs_SES %>% group_by(species) %>% summarise(mean_SES = mean(SES, na.rm = T)) # susceptibility to warming

sgnf_SES <- traits4 %>% filter(SES >= 1 | SES <= -1) %>% group_by(species) %>% summarise(sgnf_SES = n())

species_sd <- species_sd %>% left_join(species_n, by = "species") %>% left_join(distribution, by = "species") %>% left_join(mean_abs_SES, by = "species") %>% left_join(sgnf_SES, by = "species")

rm(traits_scaled, species_n, distribution, raw_traits, mean_abs_SES, sgnf_SES)

```

# DEPRECTAED
```{r}
# d13c only has negative values while d15n has positive and negative values
# Somehow for d15n, values range around 0 so relative sd makes no sense as mean = 0 and sd = 1 ..
# Instead, use e.g. MAD mean absolute deviation. 1/n * sum(abs(x-mean)). That doesnt solve the problem. The problem is that traits have different units of measurement. To be able to compare variation between traits, I divide sd by mean which is not possible for d15n. Instead, scale the traits seperately (?)
# Computation of Cohen's d is not affected by values ranging around 0

species_mad <- aggregate(traits$value, by = traits[,4:5],
                         FUN = function(x) ie2misc::madstat(x))
species_sd <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(var))
species_sd$x <- sqrt(species_sd$x)
species_sd <- rename(species_sd, sd = x)
species_mean <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(mean))

species_abs_SES <- traits4 %>% na.omit() %>% group_by(species) %>% summarise(mean_SES = mean(abs(SES)))

species_sd <- cbind(species_sd, species_mean[,3])
species_sd <- rename(species_sd, mean = `species_mean[, 3]`)
species_sd <- species_sd %>% mutate(rel_sd = sd / mean) #%>% select(-c(sd, mean))


rm(species_mean, species_abs_SES)
```

# plotting relationship between trait plasticity and species type
```{r}
p1 <- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_sd)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1), limits = c(0.4, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean sd per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# plotting relationship between susceptibility to warming and species type
```{r}
p2<- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_SES)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8), limits = c(0, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean absolute SES per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# t.tests
```{r}
all_cmb <- traits %>% select(-c(blockID, warming, value)) %>% group_by(siteID, species, trait) %>%
                      slice_sample(n = 1) # all combinations of sites, species and traits

out <- list() #output is list of p-values
for(i in 1:nrow(all_cmb)){ 
  tryCatch({
  cmb <- all_cmb[i,1:3]
  subset <- filter(traits,  siteID == paste(cmb[1,1]) & species == paste(cmb[1,2]) & trait == paste(cmb[1,3]))
  t_res <- t.test(subset$value ~ subset$warming)
  out[[i]]  <- paste(t_res$p.value, i)}, error = function(e){})
} # in every iteration I filter for one species, trait and site, output is list of p-values

out <- out[lapply(out, length) > 0]
t_results <- out %>% as.data.frame() %>% t() %>% as.data.frame()
t_results <- t_results %>% separate_wider_delim(V1, delim = " ", names = c("p-value", "iteration"))

all_cmb <- all_cmb %>% rownames_to_column(var = "iteration") %>% left_join(t_results, by = "iteration")
sign_cmb <- filter(all_cmb, `p-value` < 0.05)
```