---
title: "Standardized Effect Size"
author: "Joshua"
date: "2023-10-13"
output: html_document
---

# Packages
```{r echo = FALSE, print = FALSE, message = FALSE}
library("tidyverse")
library("ie2misc") # madstat mean absolute deviation
library("ggplot2")
library("gghalves")
library("cowplot")
```

# Re-arranging data frame and computing Cohen's d
```{r}
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)
chem_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_chemical_traits_2022.txt", guess_max = Inf)

chem_traits <- chem_traits %>% group_by(ID_merged, trait) %>% sample_n(1) 
chem_traits <- chem_traits %>% ungroup() %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("c_percent", "n_percent", "c_n", "d15n", "d13c")) # no sample removed, but trait phosphorus percentage removed because of missing data

traits <- raw_traits %>% select(c(siteID, blockID, warming, species, trait, value)) %>% na.omit() %>%
  filter(trait %in% c("ldmc", "leaf_area_cm2", "leaf_thickness_mm", "plant_height_cm", "sla_cm2_g")) # one sample removed: DLL3549
traits <- rbind(traits, chem_traits)

selected_sp <- traits %>% select(siteID, warming, species) %>% unique() %>% group_by(species) %>% mutate(Freq = n()) %>%
               filter(Freq >= 4 & species != "Achillea millefolium") # filtering species we have samples for in C and W for each site. n = 13. 2 sites n = 17. Not included is Achillea millefolium because it has warming samples only in Gud
selected_sp <- unique(selected_sp$species)
traits <- traits %>% filter(species %in% selected_sp) # trait set with only 17 selected species. xx.x % of data omitted
rm(chem_traits, raw_traits, selected_sp)

# aggregated by site, block and experiment____________________________________________________________________________
traits1 <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(mean))
traits1 <- rename(traits1, mean_value = x)
traits1l <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(length))
traits1l <- rename(traits1l, n_obs = x)
traits1sd <- aggregate(traits$value, by = traits[,1:5], FUN = na.omit(var)) # default: sample not population variance
traits1sd$x <- sqrt(traits1sd$x)
traits1sd <- rename(traits1sd, sd = x)

# aggregated by site and experiment__________________________________________________________________________________
traits2 <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(mean))
traits2 <- rename(traits2, mean_value = x)
traits2l <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(length))
traits2l <- rename(traits2l, n_obs = x)
traits2sd <- aggregate(traits$value, by = traits[,c(1,3:5)], FUN = na.omit(var)) # default: sample not population variance
traits2sd$x <- sqrt(traits2sd$x)
traits2sd <- rename(traits2sd, sd = x)

traits3 <- cbind(traits2, traits2l$n_obs, traits2sd$sd)
traits3 <- rename(traits3, n_obs = `traits2l$n_obs`, sd = `traits2sd$sd`)
traits3$ID <- paste(traits3$siteID, traits3$species, traits3$trait, sep = "_")
traits3C <- filter(traits3, warming == "C") # Control
traits3OTC <- filter(traits3, warming == "W") # Warming

traits3C <- traits3C %>% rename(C_mean = mean_value, C_n = n_obs, C_sd = sd) %>% select(-c(warming))
traits3OTC <- traits3OTC %>% rename(OTC_mean = mean_value, OTC_n = n_obs, OTC_sd = sd) %>%
  select(-c(siteID, species, warming, trait))

traits4 <- full_join(traits3C, traits3OTC, by = "ID")
traits4 <- select(traits4, -c(ID))
traits4 <- filter(traits4, !is.na(traits4$siteID) & !is.na(traits4$OTC_mean))
traits4 <- traits4 %>% mutate(mean_dif = C_mean - OTC_mean, n_dif = C_n - OTC_n, sd_dif = C_sd - OTC_sd)

traits4$pooled_SD <- NA
for(i in 1:nrow(traits4)) {
  traits4$pooled_SD[i] <- if(traits4$n_dif[i] == 0)
  {sqrt((traits4$C_sd[i]^2+traits4$OTC_sd[i]^2)/2)} # pooled sd for equal group sizes
  else {sqrt(((traits4$C_n[i] - 1) * traits4$C_sd[i]^2 + (traits4$OTC_n[i] - 1) * traits4$OTC_sd[i]^2) / (traits4$C_n[i] + traits4$OTC_n[i] - 2))} # pooled sd for unequal group sizes
  }

traits4$SES <- (traits4$OTC_mean - traits4$C_mean) / traits4$pooled_SD # Cohen's d: number of SDs between the two means:
 # mean(group a) - mean(group b) divided by pooled standard deviation.  https://en.wikiversity.org/wiki/Cohen%27s_d

traits4$PR <- (traits4$OTC_mean - traits4$C_mean) / traits4$C_mean # Relative Distance Plasticity Index: shows the factor by which the trait value in the OTC increased or decreased, in comparison to the control plot

traits4$trait <- case_when(traits4$trait == "leaf_area_cm2" ~ "LA", traits4$trait == "leaf_thickness_mm" ~ "LTH", traits4$trait == "sla_cm2_g" ~ "SLA", traits4$trait == "plant_height_cm" ~ "H", traits4$trait == "ldmc" ~ "LDMC", traits4$trait == "c_n" ~ "C:N", traits4$trait == "c_percent" ~ "C %", traits4$trait == "d13c" ~ "δ13C", traits4$trait == "d15n" ~ "δ15N", traits4$trait == "n_percent" ~ "N %")

traits_f <- traits4 %>% filter(!is.na(SES)) %>% group_by(trait) %>% mutate(trait_mean = mean(SES), trait_sd = sd(SES)) # trait table filtered
traits_f$outlier3 <- case_when(traits_f$SES <= traits_f$trait_mean - 3* traits_f$trait_sd ~ "low",
                               traits_f$SES >= traits_f$trait_mean + 3* traits_f$trait_sd ~ "high") # 6 outliers +- 3 sd away from the mean removed
traits_f <- traits_f %>% filter(is.na(outlier3)) %>% select(-c(trait_mean, trait_sd, outlier3))

rm(traits1, traits1l, traits1sd, traits2, traits2l, traits2sd, traits3, traits3C, traits3OTC, i)
```

#Species trait tables
```{r}
#n_obs <- traits4 %>% filter(!is.na(SES)) %>% group_by(siteID, trait) %>% mutate(n_obs = n()) %>% sample_n(1) %>% select(siteID, trait, n_obs)

species_SES_table <- traits_f %>% group_by(species, trait) %>% mutate(mean_SES = mean(SES)) %>%
  select(species, trait, mean_SES) %>% sample_n(1) %>%
  pivot_wider(names_from = trait, values_from = mean_SES)
species_SES_table$mean_overall <- rowMeans(abs(species_SES_table[,2:11]), na.rm = TRUE)

trait_SES_table <- traits_f  %>% group_by(trait) %>% mutate(meanSES = mean(SES), absSES = mean(abs(SES)), nsamples = n()) %>%
                   sample_n(1) %>% ungroup() %>% select(c(trait, meanSES, absSES, nsamples))

#_______________________________________________________________________________
sp_tables <- traits_f  %>% select(siteID, species, trait, SES) #%>% filter(trait != "C:N")

data_all_sites <- sp_tables %>% mutate(siteID = "overall") %>% group_by(species, trait) %>% mutate(SES = mean(SES)) %>% sample_n(1) %>% ungroup()
sp_tables <- sp_tables %>% bind_rows(data_all_sites)
sp_tables$precip <- case_when(sp_tables$siteID == "Ulvehaugen" ~ "low", sp_tables$siteID == "Gudmedalen" ~ "medium",
                                 sp_tables$siteID == "Skjelingahaugen" ~ "high", sp_tables$siteID == "overall" ~ "overall")
sp_tables <- sp_tables %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall"))) %>% select(-c(siteID))
#sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", "Astragalus alpinus", "Bistorta vivipara", "Carex bigelowii", "Poa alpina", "Salix herbacea", "Saussurea alpina", "Sibbaldia procumbens", "Thalictrum alpinum", "Veronica alpina", "Viola biflora", "Agrostis capillaris", "Anthoxanthum odoratum", "Campanula rotundifolia", "Carex vaginata", "Leontodon autumnalis", "Nardus stricta")))

sp_tables <- sp_tables %>% mutate(species = factor(species, levels = c("Alchemilla alpina", "Astragalus alpinus", "Bistorta vivipara", "Campanula rotundifolia", "Leontodon autumnalis", "Salix herbacea", "Saussurea alpina", "Sibbaldia procumbens", "Thalictrum alpinum", "Veronica alpina", "Viola biflora", "Agrostis capillaris", "Anthoxanthum odoratum", "Carex bigelowii", "Carex vaginata", "Nardus stricta", "Poa alpina")))

points_plot <- ggplot(sp_tables, aes(x = precip, y = species, size = abs(SES), color = SES > 0)) + geom_point() +
  scale_color_manual(values = c("red", "blue"), labels = c("negative", "positive")) +
  scale_size_continuous(range = c(0.5,6), breaks = c(0.1, 1, 2, 3)) + # c(1, 10)
  scale_y_discrete(limits = rev(levels(sp_tables$species))) + theme_classic() +
  labs(title = NULL, x = "Precipitation", y = NULL, size = "Standardized effect size [Cohen's d]", color = NULL) +
  geom_hline(aes(yintercept = 6.5), lty = 2, linewidth = 0.25) +
  facet_wrap(~ trait, ncol = 4) + # scales = "free"
  annotate("text", x = 4.3, y = 8.7, label = "Forbs 🡺" , angle = 90, size = 4) + # "Alpine 🡺"
  annotate("text", x = 4.3, y = 3.7, label = "Graminoids", angle = 90, size = 4) + # "🡸 Generalist" # or just "Graminoids"
  annotate("rect", xmin = 3.5, xmax = 4.5, ymin = -Inf, ymax = Inf, fill = "grey", alpha = 0.2) +
  theme(legend.position = "top", strip.text = element_text(size = 10, face = "bold"),
        axis.title = element_text(size = 12), panel.border = element_rect(colour = "black", fill = NA, linewidth = 1))
# print 800 x 1000
# Helpful Unicode tables for arrows: https://en.wikipedia.org/wiki/Arrow_(symbol)


rm(sp_tables, data_all_sites)
```

# Testing for differences using t-tests and f-tests
```{r}
classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)
classification$Type <- case_when(str_detect(classification$species, "Agrostis|Anthoxanthum|Carex|Festuca|Poa|Avenella|Deschampsia|Nardus") ~ "Graminoids", TRUE ~ "Forbs")

# comparison alpine vs generalist species and graminoids vs. Forbs
SES_compare <- traits_f %>% select(siteID, species, trait, SES) %>% left_join(classification, by = "species")
#SES_compare$SES <- abs(SES_compare$SES) # Optional. Depending if you want to compare actual or absolute SES values
t_test_results <- SES_compare %>% do(t_test = t.test(SES ~ as.factor(alpine), data = .)) %>% ungroup()

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value) 
test <- SES_compare %>% group_by(trait, alpine) %>% summarize(mean = mean(abs(SES))) # shows trait means by group

print(p_values)

var_test_results <- SES_compare %>% do(var_test = var.test(SES ~ factor(alpine, levels = c(1, 0)), data = .)) %>% ungroup() # alternatively: factor(alpine, levels = c(0, 1))
var_test_summary <- var_test_results %>% mutate(
    f_statistic = sapply(var_test, function(x) x$statistic), # f-statistic and ratio of variances are the same.
    df1 = sapply(var_test, function(x) x$parameter[1]),
    df2 = sapply(var_test, function(x) x$parameter[2]),
    p_value = sapply(var_test, function(x) x$p.value)) %>%
  select(trait, f_statistic, df1, df2, p_value)


#_______________________________________________________________________________

site_comp <- traits_f %>% mutate(comp1 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Gudmedalen" ~ "Gud"),
                                  comp2 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Skjelingahaugen" ~ "Skj"),
                                  comp3 = case_when(siteID == "Gudmedalen" ~ "Gud", siteID == "Skjelingahaugen" ~ "Skj"))
comp2 <- site_comp %>% select(-c(comp1, comp3)) %>% na.omit() %>% group_by(trait)
t_test_results <- comp3 %>% do(t_test = t.test(SES ~ as.factor(comp3), data = .)) %>% ungroup()

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value) 
test <- comp1 %>% group_by(trait, comp1) %>% summarize(mean = mean(trait_mean)) # shows trait means by group

print(p_values)

```


# Summarizing patterns
```{r}
classification <- read_tsv("../Input data/species classifications.txt", guess_max = Inf) # table that contains classification (alpine vs. generalist)
classification$Type <- case_when(str_detect(classification$species, "Agrostis|Anthoxanthum|Carex|Festuca|Poa|Avenella|Deschampsia|Nardus") ~ "Graminoids", TRUE ~ "Forbs")

# species with most medium to high effect sizes, alpine vs. generalists
SES_lim <- traits_f %>% select(siteID, species, trait, SES) %>% group_by(species)
SES_lim <- SES_lim %>% summarize(total = n(), limit_1 = sum(abs(SES) >= 1), limit_08 = sum(abs(SES) >= 0.8), limit_05 = sum(abs(SES) >= 0.5))
SES_lim <- SES_lim %>% left_join(classification[,1:4], by = "species") %>% mutate(alpine = str_replace_all(alpine, c("1" = "Alpine", "0" = "Generalist")))

alp_gen <- SES_lim %>% group_by(Type) %>% summarize(across(2:5, sum))
alp_gen <- alp_gen %>% mutate(limit_08 = limit_08 - limit_1, limit_05 = limit_05 - (limit_08 + limit_1),
                              total = total - (limit_05 + limit_08 + limit_1)) %>%
           pivot_longer(cols = 2:5, names_to = "Category", values_to = "Value") %>% ungroup() # changing counts so that each column contains only the surplus
alp_gen$Category <- factor(alp_gen$Category, levels = c("total", "limit_05", "limit_08", "limit_1"))

bar_plot <- ggplot(alp_gen, aes(x = Type, y = Value, fill = Category)) +
  geom_bar(stat = "identity", width = 0.7, color = "black") + # or position = "dodge" # or without position and alpha, as stacked graph # 
  scale_fill_manual(values = c("white", "lightgrey", "darkgrey", "black"), labels = c("SES < 0.5", "SES \u2265 0.5", "SES \u2265 0.8", "SES \u2265 1")) +
  facet_wrap(~ Type, scales = "free", ncol = 2) +
  labs(title = NULL, x = "", y = "Number of paired observations") +
  theme_classic() + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank()) # print 400 x 400

#SES_lim$fraction <- SES_lim$sum_SES05/SES_lim$total # the fraction is important because there are more alpine than generalist species

#histograms
hist_table <- traits_f %>% ungroup() %>% select(species, SES) %>% left_join(classification[,1:4], by = "species") %>%
  mutate(Group = str_replace_all(alpine, c("1" = "Alpine", "0" = "Generalist")))
hist_table$Type <- factor(hist_table$Type, levels = c("Forbs", "Graminoids"))

percentiles <- aggregate(SES ~ Type, data = hist_table, function(x) c(mean = mean(x), Q05 = quantile(x, 0.05), Q95 = quantile(x, 0.95)))
percentiles <- do.call(data.frame, percentiles) # Flatten the nested columns
colnames(percentiles) <- c("Group", "mean", "Q05", "Q95")

hist_plot <- ggplot(hist_table, aes(x = SES, fill = Type)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 30, color = "black") +
  geom_vline(data = percentiles, aes(xintercept = mean), linetype = "dashed", linewidth = 1, color = c("black", "red")) +
  geom_vline(data = percentiles, aes(xintercept = Q05, color = Type), linetype = "dotted", linewidth = 1, color = c("black", "red")) +
  geom_vline(data = percentiles, aes(xintercept = Q95, color = Type), linetype = "dotted", linewidth = 1, color = c("black", "red")) +
  scale_fill_manual(values = c("darkgrey", "red")) +
  scale_color_manual(values = c("darkgrey", "red")) +
  labs(title = NULL, x = "Cohen's d", y = "Number of paired observations") +
  theme_classic() +
  theme(legend.position = "top")

combined_plot <- plot_grid(hist_plot, bar_plot, labels = c("a", "b"), ncol = 2, align = "h", axis =  "tb", rel_widths = c(3, 2)) # print 850 x 400
```

# Plotting SES values: Violin plots
```{r}
SES_sites <- traits_f %>% select(siteID, species, trait, SES)

SES_sites$precip <- case_when(SES_sites$siteID == "Ulvehaugen" ~ "low", SES_sites$siteID == "Gudmedalen" ~ "medium", SES_sites$siteID == "Skjelingahaugen" ~ "high")

data_all_sites <- SES_sites %>% mutate(precip = "overall")
SES_combined <- bind_rows(SES_sites, data_all_sites)
SES_combined <- SES_combined %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall")))

SES_mean <- SES_combined %>% group_by(precip, trait) %>% summarize(mean_SES = mean(SES), .groups = "drop")

# Are mean SES values significantly different from 0?
t_tests <- SES_combined %>% select(-c(siteID, species)) %>% group_by(precip, trait) %>%
  summarise(t_test = list(t.test(SES, mu = 0)), .groups = "drop") %>%  # Perform t-test against 0
  mutate(estimate = map_dbl(t_test, ~ .x$estimate),  # Extract mean SES
         t_value = map_dbl(t_test, ~ .x$statistic),  # Extract t-statistic
         p_value = map_dbl(t_test, ~ .x$p.value)     # Extract p-value
  ) %>% select(-t_test)

SES_mean <- left_join(SES_mean, t_tests[,c(1:2,5)], by = c("precip", "trait"))
SES_mean <- SES_mean %>% mutate(significance = case_when(p_value < 0.05 ~ "🞲", p_value < 0.1  ~ "+", TRUE ~ ""),
                                label_text = paste0(round(mean_SES, 2), " ", significance))

violin_plot <- ggplot(SES_combined, aes(x = precip, y = SES, fill = precip)) +
  geom_half_violin(side = "l", trim = TRUE, color = NA) +
  geom_half_point(side = "r", position = position_jitter(width = 0), alpha = 0.5, shape = 16) +
  geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
  geom_text(data = SES_mean, aes(x = precip, y = label_text, label = label_text), y = 1.9, vjust = -1, size = 3.5) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "black", linewidth = 1) +
  facet_wrap(~ trait, scales = "free", ncol = 2) + # Facet by trait
  scale_fill_manual(values = c("#c6dbef", "#6baed6", "#08519c", "grey")) +
  theme_classic() +
  labs(title = NULL, x = "Precipitation", y = "Standardized effect size [Cohen's d]") +
  theme(legend.position = "none", strip.text = element_text(size = 10, face = "bold"), axis.title = element_text(size = 12)) +
  ylim(-2.62, 2.62) # otherwise ylim(-5,5)

# print 800 x 1000

#_______________________________________________________________________________ violin plots for all traits and across sites
#multi_bp <- ggplot(SES_sites, aes(x = trait, y = SES, group = trait)) + geom_violin(aes(fill = trait), trim = T) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) + stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
#               colour = "black") + ylim(-2.5,2.5) + geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.1)
# + geom_boxplot(aes(fill = trait), outlier.alpha = 0)

#_______________________________________________________________________________ violin plots for all traits and across sites but with mean values for species
#SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(2,3)], FUN = mean)
#SES_sites <- SES_sites %>% rename(`mean SES` = x)

#multi_bp <- ggplot(SES_sites, aes(x = trait, y = `mean SES`, group = trait)) +
#  geom_boxplot(aes(fill = trait), outlier.alpha = 0) +
#  theme_classic() + geom_hline(yintercept = 0, lty = 2, linewidth = 0.25) +
#  geom_jitter(color = "black", height = NULL, width = 0.3, alpha = 0.5) + ylim(-2.5,2)
```

# Functional differences between sites (trait means)
```{r}
site_comp <- traits %>% filter(warming == "C") %>% group_by(siteID, species, trait) %>%
             summarize(trait_mean = mean(value)) %>% ungroup() # site comparisons. 23 trait measurements missing.

site_comp$trait <- case_when(site_comp$trait == "leaf_area_cm2" ~ "LA", site_comp$trait == "leaf_thickness_mm" ~ "LTH", site_comp$trait == "sla_cm2_g" ~ "SLA", site_comp$trait == "plant_height_cm" ~ "H", site_comp$trait == "ldmc" ~ "LDMC", site_comp$trait == "c_n" ~ "C:N", site_comp$trait == "c_percent" ~ "C %", site_comp$trait == "d13c" ~ "δ13C", site_comp$trait == "d15n" ~ "δ15N", site_comp$trait == "n_percent" ~ "N %")

site_comp <- site_comp %>% group_by(species, trait) %>% mutate(Freq = n()) %>% ungroup()
site_comp <- site_comp %>% filter(Freq == 3) %>% select(-c(Freq)) # filtering out incomplete trait measurements (not in all 3 sites)
test <- as.data.frame(table(site_comp$trait))

site_comp$precip <- case_when(site_comp$siteID == "Ulvehaugen" ~ "low", site_comp$siteID == "Gudmedalen" ~ "medium", site_comp$siteID == "Skjelingahaugen" ~ "high")

data_all_sites <- site_comp %>% mutate(precip = "overall")
data_combined <- bind_rows(site_comp, data_all_sites)
data_combined <- data_combined %>% mutate(precip = factor(precip, levels = c("low", "medium", "high", "overall")))

mean_across <- data_combined %>% group_by(precip, trait) %>% summarize(overall_mean = mean(trait_mean), .groups = "drop")

violin_plot <- ggplot(data_combined, aes(x = precip, y = trait_mean, fill = precip)) +
  geom_half_violin(side = "l", trim = TRUE, color = NA) +
  geom_half_point(side = "r", position = position_jitter(width = 0), alpha = 0.5, shape = 16) +
  geom_hline(data = filter(mean_across, precip == "overall"), aes(yintercept = overall_mean), lty = 2, linewidth = 0.25) +
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange", colour = "black", linewidth = 1) +
  facet_wrap(~ trait, scales = "free", ncol = 2) + # Facet by trait
  scale_fill_manual(values = c("#c6dbef", "#6baed6", "#08519c", "grey")) +
  theme_classic() +
  labs(title = NULL, x = "Precipitation", y = "Trait means") +
  theme(legend.position = "none", strip.text = element_text(size = 10, face = "bold"), axis.title = element_text(size = 12))
  #ylim(-2.62, 2.62) # otherwise ylim(-5,5)

# print 800 x 1000

site_comp <- site_comp %>% mutate(comp1 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Gudmedalen" ~ "Gud"),
                                  comp2 = case_when(siteID == "Ulvehaugen" ~ "Ulv", siteID == "Skjelingahaugen" ~ "Skj"),
                                  comp3 = case_when(siteID == "Gudmedalen" ~ "Gud", siteID == "Skjelingahaugen" ~ "Skj"))
comp3 <- site_comp %>% select(-c(comp1, comp2)) %>% na.omit() %>% group_by(trait)
t_test_results <- comp3 %>% do(t_test = t.test(trait_mean ~ as.factor(comp3), data = .)) %>% ungroup()

p_values <- t_test_results %>% mutate(p_value = sapply(t_test, function(x) x$p.value)) %>% select(trait, p_value) 
test <- comp1 %>% group_by(trait, comp1) %>% summarize(mean = mean(trait_mean)) # shows trait means by group

print(p_values)
# Significant differences: Ulv Gud only D13C, p = 0.05397769
# Ulv Skj only C % p = 0.01907241	
# Gud Skj H p = 0.00504747
rm(mean_across, data_combined, data_all_sites, test)
```

# Plotting SES values
```{r}
SES_sites <- traits4 %>% select(c(1:3,5,8,14)) %>% na.omit()

SES_sites <- aggregate(SES_sites$SES, by = SES_sites[,c(1,3)], FUN = mean)
SES_sites <- SES_sites %>% rename(`mean SES` = x)
SES_sites$level <- case_when(SES_sites$`mean SES` < 0 ~ "negative", SES_sites$`mean SES` > 0 ~ "positive")

test <- SES_sites %>% group_by(trait) %>% mutate(mean_trait = mean(`mean SES`)) %>% sample_n(1) %>% select(c(trait, mean_trait))

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Ulvehaugen", "Gudmedalen", "Skjelingahaugen"))
SES_sites$trait <- factor(SES_sites$trait, levels = c("C %", "N %", "C:N", "δ13C", "δ15N", "H", "LA", "LDMC", "LTH", "SLA"))

SES_plot <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, shape = level)) +  
  geom_point(size = 3) +
  scale_shape_manual(values = c(1, 16)) +
  geom_hline(yintercept = 0, lty = 2, size = 0.25) +
  coord_flip() +
  xlab("") + ylab("Absolute Cohen's d") +
  theme_bw() +
  guides(colour = "legend", shape = "none") +
  facet_grid(. ~ trait) +
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        legend.title = element_blank(),
        legend.position= "top",
        legend.text = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        axis.text.x = element_text(angle=45, vjust=.5, size = 16),
        axis.text.y = element_text(vjust=.5, size = 16),
        strip.text = element_text(size = 16, face = "bold"))

# print 1200 x 400

SES_sites$siteID <- factor(SES_sites$siteID, levels = c("Skjelingahaugen", "Gudmedalen", "Ulvehaugen"))

SES_plot2 <- ggplot(SES_sites, aes(x = siteID, y = `mean SES`, group = trait)) +
  geom_line(aes(color = trait), linewidth = 1, alpha = 0.5) +
  geom_point(aes(color = trait), size = 2) +
  theme_classic() + xlab("") + ylab("Absolute Cohen's d") +
  theme(axis.title.y = element_text(size = 14),
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 14, face = "bold"))
# print 600 x 400
```

# Species specific plasticity and succeptibility to warming
```{r}
# Species without paired observations (inside and outside OTC) are omitted!!
distribution <- readr::read_tsv("../Input data/species classifications.txt", guess_max = Inf)
raw_traits <- readr::read_tsv("../Input data/PFTC6_Incline_clean_leaf_traits_2022.txt", guess_max = Inf)

traits_scaled <- traits %>% as.data.frame() %>% select(species, trait, value)
traits_scaled <- traits_scaled %>% semi_join(filter(traits4, !is.na(SES)), by = "species") # remove species without SES values
traits_scaled <- traits_scaled %>% group_by(trait) %>% mutate(scaled_values = scale(value, center = T, scale = T)) %>% ungroup()

species_sd <- aggregate(traits_scaled$scaled_values, by = traits_scaled[,1:2], FUN = na.omit(var))
species_sd$V1 <- sqrt(species_sd$V1)
species_sd <- rename(species_sd, sd = V1)
species_sd <- species_sd %>% group_by(species) %>% summarise(mean_sd = mean(sd, na.rm = T))

species_n <- raw_traits %>% group_by(ID) %>% select(c(species, ID)) %>% slice_sample(n = 1)
species_n <- as.data.frame(table(species_n$species))
species_n <- rename(species_n, species = Var1)

mean_abs_SES <- traits4 %>% select(species, SES) %>% na.omit() %>% mutate(SES = abs(SES)) # mean absolute SES per species
mean_abs_SES <- mean_abs_SES %>% group_by(species) %>% summarise(mean_SES = mean(SES, na.rm = T)) # susceptibility to warming

sgnf_SES <- traits4 %>% filter(SES >= 1 | SES <= -1) %>% group_by(species) %>% summarise(sgnf_SES = n())

species_sd <- species_sd %>% left_join(species_n, by = "species") %>% left_join(distribution, by = "species") %>% left_join(mean_abs_SES, by = "species") %>% left_join(sgnf_SES, by = "species")

rm(traits_scaled, species_n, distribution, raw_traits, mean_abs_SES, sgnf_SES)

```

# DEPRECTAED
```{r}
# δ13c only has negative values while δ15N has positive and negative values
# Somehow for δ15N, values range around 0 so relative sd makes no sense as mean = 0 and sd = 1 ..
# Instead, use e.g. MAD mean absolute deviation. 1/n * sum(abs(x-mean)). That doesnt solve the problem. The problem is that traits have different units of measurement. To be able to compare variation between traits, I divide sd by mean which is not possible for δ15N. Instead, scale the traits seperately (?)
# Computation of Cohen's d is not affected by values ranging around 0

species_mad <- aggregate(traits$value, by = traits[,4:5],
                         FUN = function(x) ie2misc::madstat(x))
species_sd <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(var))
species_sd$x <- sqrt(species_sd$x)
species_sd <- rename(species_sd, sd = x)
species_mean <- aggregate(traits$value, by = traits[,4:5], FUN = na.omit(mean))

species_abs_SES <- traits4 %>% na.omit() %>% group_by(species) %>% summarise(mean_SES = mean(abs(SES)))

species_sd <- cbind(species_sd, species_mean[,3])
species_sd <- rename(species_sd, mean = `species_mean[, 3]`)
species_sd <- species_sd %>% mutate(rel_sd = sd / mean) #%>% select(-c(sd, mean))


rm(species_mean, species_abs_SES)
```

# plotting relationship between trait plasticity and species type
```{r}
p1 <- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_sd)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1), limits = c(0.4, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean sd per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# plotting relationship between susceptibility to warming and species type
```{r}
p2<- ggplot(species_sd, aes(x = as.factor(alpine), y = mean_SES)) + geom_boxplot(outlier.alpha = 0) + theme_classic() +
  geom_jitter(width = 0.3, height = 0, alpha = 0.3) +
  scale_y_continuous(breaks = c(0, 0.2, 0.4, 0.6, 0.8), limits = c(0, 1)) +
  scale_x_discrete(labels = c("Generalist", "Alpine")) + xlab("") + ylab("Mean absolute SES per species") +
  theme(axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
# print 350 x 400

```

# t.tests
```{r}
all_cmb <- traits %>% select(-c(blockID, warming, value)) %>% group_by(siteID, species, trait) %>%
                      slice_sample(n = 1) # all combinations of sites, species and traits

out <- list() #output is list of p-values
for(i in 1:nrow(all_cmb)){ 
  tryCatch({
  cmb <- all_cmb[i,1:3]
  subset <- filter(traits,  siteID == paste(cmb[1,1]) & species == paste(cmb[1,2]) & trait == paste(cmb[1,3]))
  t_res <- t.test(subset$value ~ subset$warming)
  out[[i]]  <- paste(t_res$p.value, i)}, error = function(e){})
} # in every iteration I filter for one species, trait and site, output is list of p-values

out <- out[lapply(out, length) > 0]
t_results <- out %>% as.data.frame() %>% t() %>% as.data.frame()
t_results <- t_results %>% separate_wider_delim(V1, delim = " ", names = c("p-value", "iteration"))

all_cmb <- all_cmb %>% rownames_to_column(var = "iteration") %>% left_join(t_results, by = "iteration")
sign_cmb <- filter(all_cmb, `p-value` < 0.05)
```